---
title: "Reproduciblity LASSO and Bayesian LASSO Regression for Directional Response (d=3)"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Loading the R Package
```{r }
library(RBVNF)
load_packages()
load_additional_packages()
library(glmnet)
```



## Simulated Data Generation and EM for Posterior Mode (d=3, Spherical Data):
In this part of the demonstration, we generate a dataset of size n=500, with p=20 (20 covariates) and the responses are circular,i.e., d=3. Then we Bayesian-LASSO algorithm to estimate the regression coefficients, where we consider the inverse Gamma Prior and sample the tuning parameter.

# LASSO Regression For Directional Data (d=3):

```{r }

Start_time=Sys.time()
n=500  # NUmber of the samples
p=20    # NUmber of the regression covariates
d=3   # Number of direcions in the direcional data

Num_of_nonzero_beta= round(p*.10)
Min_Non_Zero_beta= 1
Max_Non_Zero_beta=10
data_lst<-Data_generator_vnf_reg_sparse(n=n,
                                          p=p,
                                          d=d,
                                          SetUp = 3,
                                          NumOfNonZeroBeta=c(Num_of_nonzero_beta,
                                                             Min_Non_Zero_beta,
                                                             Max_Non_Zero_beta
                                                             )
                                          )
```


```{r }
MCMC_Sample_Size=2000# 
 lst_BLASSO_Beta_MCMC  =               MCMC_BLASSO_Dir_regression_sampler_V1( Y=data_lst$Y,
                                                                                 X=data_lst$X,
                                                                                 prior=NULL,
                                                                                 beta_init = NULL,
                                                                                 MCSamplerSize =MCMC_Sample_Size,
                                                                                 lasso_lambda_spec = list(
                                                                                                            Type="SAMPLE",
                                                                                                            lasso_lambda=0.01,
                                                                                                                 hyper_lambda_selector= NULL
                                                                                                          ))
    

                                                                              lst=lst_BLASSO_Beta_MCMC
  i=1;j= 1
  Plot_MCMC_Diag_Triplet(lst$MC$Mc_Beta[,i,j],y_lab_text = bquote(beta[.(i)][.(j)]))
  Posterior_mean=apply(lst$MC$Mc_Beta, MARGIN = c(2,3), FUN = mean)
  Posterior_Q_Lower=apply(lst$MC$Mc_Beta, MARGIN = c(2,3), FUN = function(x){return(c(quantile(x, probs = .025)))} )
  Posterior_Q_Upper=apply(lst$MC$Mc_Beta, MARGIN = c(2,3), FUN = function(x){return(c(quantile(x, probs = .975)))})
print(cbind(TrueValue=c(t(data_lst$beta)), Posterior_mean=c(t(Posterior_mean)),Lower_Bound=c(t(Posterior_Q_Lower)), Upper_Bound=c(t(Posterior_Q_Upper) )))
  
  # Samples of the tuning parameter
  Plot_MCMC_Diag_Triplet(lst$MC$lasso_lambda_all,y_lab_text = bquote(lambda))
                                                                                                
```



```{r }

plot_beta_p_20_d_3<-function(Mc_obj=Mc_obj_lso, burnIN=1000, PlotType="vio", zero_marking_linetype=6, zero_marking_linewidth=.8){


  #location="/Users/subhadippal/Desktop/Lasso_Simulation_RBVNF/"
  #fileName= paste0("MC_SIM_BLASSO_Reg_Dir_Data_d_eq_",2,"_SimNUmber_",5,".RData")
  #file_with_path= paste0(location,fileName)
  #assign('Mc_obj_lso', get( load(file=file_with_path ) ))

  #plot_beta_p_20_d_2(Mc_obj_lso)

  data_summary <- function(x) {
    m <- median(x)
    ymin <- as.numeric(quantile(x,.025))#m-sd(x)
    ymax <- as.numeric(quantile(x, 0.975))#m+sd(x)
    return(c(y=m,ymin=ymin,ymax=ymax))
  }

  Mc_Beta_burnin<-((Mc_obj$MC_lst$MC$Mc_Beta[-(1:burnIN), , ]))
  mc_samples= Mc_Beta_burnin
  mc_len=dim(mc_samples)[1]
  value1 <- ( matrix(mc_samples, nrow=mc_len  ))

  index_rearrange=0*1:60
  for(i in 1:20){
    index_rearrange[3*i-2]= i; index_rearrange[3*i-1]= 20+i; index_rearrange[3*i]= 40+i
  }
  value= value1[,index_rearrange]
  #names <- c(rep("A", mc_len) , rep("B", 5) , rep("C", 30), rep("D", 100))
  beta_names<-c(t(replicate(1, paste0("beta",paste0('[paste(',row(mc_samples[1, , ]), ",',',",col(mc_samples[1, , ]), ')]')))))[index_rearrange]
  beta= c(t(replicate(mc_len, paste0("beta", 111:170))))
  #beta<-c(t(replicate(mc_len, paste0("beta",paste0('[paste(',row(mc_samples[1, , ]), ",',',",col(mc_samples[1, , ]), ')]')))))
  #browser()
  data <- data.frame(Names=c(beta),Value=c(value))

  # prepare a special xlab with the number of obs for each group
  my_xlab <- paste0("c(", ((paste("expression(",(beta_names),")",collapse=","))), ")")

  # plot


  p<-ggplot(data, aes(x=Names, y=Value,fill=Names ))
  if(PlotType=='vio'){
    p<-p+with_shadow(geom_hline(yintercept=0, col="white",linewidth=zero_marking_linewidth, linetype=zero_marking_linetype ),  sigma = 1,
                     x_offset = 0,
                     y_offset = 0,
                     colour = "black" )
    p<-p+  with_shadow(geom_violin(alpha=0.9,
                                   linewidth = .05, scale = 'width'),
                       sigma = 3,
                       x_offset = 0,
                       y_offset = 0,
                       colour = "black" )
    #p<-p+stat_summary(fun.data=mean_sdl, mult=1, geom="pointrange", color="red")
    p<- p + with_shadow(stat_summary(fun.data=data_summary, size=.01, col="black"),  sigma = 2,
                        x_offset = 0,
                        y_offset = 0,
                        colour = "black" )

  }
  if(PlotType!='vio'){
    p<-p+  with_shadow(geom_boxplot(alpha=0.85,
                                    linewidth = .15,
                                    outlier.size = .05, outlier.colour = "black"),
                       sigma = 2,
                       x_offset = 0,
                       y_offset = 0,
                       colour = "black" )
  }

  p<-p+theme(legend.position="none") +scale_x_discrete(labels=eval(parse(text=my_xlab)))
  p<-p+theme(panel.grid = element_line(color = "white",
                                       size = 0.15,
                                       linetype = 1))

  p<-p+scale_fill_manual(values=c(replicate(6, "white"), replicate(54, "gray")))
  p<-p+xlab("Regression Coefficients")+ ylab(" ")+ ggtitle(" ")
  return(p)
}

```


Estimated Regression coefficients:
```{r }
Mc_obj=list(MC_lst=lst_BLASSO_Beta_MCMC)
plt_vio<-plot_beta_p_20_d_3(Mc_obj, PlotType = 'vio', zero_marking_linetype=6, zero_marking_linewidth=.5)
plt_vio
plt_box<-plot_beta_p_20_d_3(Mc_obj, PlotType = 'box', zero_marking_linetype=6, zero_marking_linewidth=.5)
plt_box

```



# Cross Validation and LASSO Estimate:
```{r }
library(glmnet)
n=500    # Number of the samples
p=30      # Number of the regression covariates
d=6    # Number of directions in the directional data

#Test Lasso
data_lst  <-  Data_generator_vnf_reg_sparse(n=200, p=p, d=d,SetUp = 2, NumOfNonZeroBeta=c(4, 1, 10))



Y = data_lst$Y;X=data_lst$X;



cv_LASSO_output<-EM_BLASSO_Dir_regression_optimizer_V1.cv(Y=data_lst$Y,
                                                         X=data_lst$X,
                                                         beta_init = NULL,
                                                         Max_EM_iter=1000,
                                                         cv_k_fold = 8,
                                                         cv_lambda_n = 40,
                                                         epsilon_lambda_range_min = .0001,
                                                         lambda_Range_Type = 2
                                                         )
                                                      

plot.cv.Dir_Lasso_Reg(cv_LASSO_output)
library(ggfx)
plt_cv_lambda<-plot.cv.Dir_Lasso_Reg_gg(cv_LASSO_output, color_theme = 2)
plt_cv_lambda

```


```{r }


beta_EM_Lasso_lambda_min=EM_BLASSO_Dir_regression_optimizer_V1(Y=data_lst$Y, X=data_lst$X, beta_init = NULL, lasso_lambda = max(cv_LASSO_output$lambda.min),   EM_tolerence = .00001)

beta_EM_Lasso_lambda1.se=EM_BLASSO_Dir_regression_optimizer_V1(Y=data_lst$Y, X=data_lst$X, beta_init = NULL, lasso_lambda = max(cv_LASSO_output$lambda.1se),   EM_tolerence = .00001)


print(cbind(TrueValue=c(t(data_lst$beta)),  beta_EM_Lasso_lambda_min=c(t(beta_EM_Lasso_lambda_min)), beta_EM_Lasso_lambda1.se=c(t(beta_EM_Lasso_lambda1.se))   ))
End_Time=Sys.time()

print(paste0("Total Run Time: ", End_Time-Start_time, "minutes"))

```



